On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-20 paper/paper.tex
Abstract for reviewers

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  %Say what problem is
  The data flow in deeply embedded domain specific langauges  falls out naturally.

  Capturing control flow in embbed
  is critical for 
  Using a deep embedding of 
 Programs that write programs 
  Sometimes,  
Embedded Domain Specific Languages are the killer app of functional languages.
%Say why it is an interesting problem
Languages with reification of code fragments allows
for high-level abstractions that directly support
diverse applications incuding machine learning and hardware description generation.
% 
  Haskell in particual has been used for many embeded code generators, such
as Lava, SunRoof, Conal work, CCC, AD, ... (finally tagless) diagrams?
%Say what our solution achieves
In this paper, we expand the capabilies of traditional,
Haskell-based, deep embeddings with a compiler extension
for capturing the useful abstraction of pattern matching. 
%Here is why the world will be a better place
With this new support, the Haskell that we capture for expressing
embededed-based solutions can be cleaner, more Haskell idiomatic,
and more declaritive in nature.

  Domain specific languages (DSLs) provide a powerful tool for abstracting over
  a class of problems.
  This
  representation is mechanized through the use of GHC Generics and a GHC Core plugin.
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedding Domain Specific Languages,
  clunkly workarounds must be employed which will be less familiar
  than the builtin control flow mechanisms of the host language.  
% Say why it is an interesting problem
  However, capturing control flow in an embedded domain specific language is crucial for
  writing programs in a natural style, and enables the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilies of traditional,
  Haskell-based, deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languges can be cleaner, more Haskell idiomatic,
  and more declarative in nature.

\end{abstract}
